\textcolor{red}{Disambiguating Monocular Depth Estimation with a Single Transient}

### 2020-02-28 paper/eccv2020/sections/hardware.tex
Moving figures around, adding edit red text.
pass over paper

% The laser operates at 450~nm with a pulse repetition rate of 25~MHz with a peak power of 450~mW and average power of 0.5~mW.

@@

\begin{figure}[t]
	\centering
  \includegraphics[width=0.8\columnwidth]{scanned_diffuse.pdf}
  \caption{Scene and measurements for diffused and summed scanned mode. The observed
    counts in the diffuse mode match closely with the sum of the raster-scanned
    measurements.}
  \label{fig:scanned_diffuse}
  % \vspace{-0.5em}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Experimental Results}

@@

\begin{figure}[t]
	\centering
  \includegraphics[width=0.8\columnwidth]{prototype_single_col.pdf}
  \caption{Prototype scanning setup. The pulsed light from the laser travels
    through a beam splitter before being guided by the galvo to the scene.
    Returning light is measured by the single-pixel SPAD. The Kinect v2 RGB 
    camera is used to capture the image used to generate the monocular depth estimate
    (the depth camera is not used).}
  \label{fig:prototype}
  % \vspace{-0.5em}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{captured.pdf}
	\caption{Experimental results. For each scene, we record a ground truth depth
    map that is raster-scanned with the SPAD (upper left subimages), and an RGB
    image (lower left). A monocular depth CNN predicts an initial depth map (top
    middle), which is corrected with the diffused SPAD histogram using the
    proposed method (top right), as shown by the error maps and root mean
    squared error (RMSE) for each example (lower center, right). The CNN is
    confused when we show it a photograph of a poster (bottom scene); it
    incorrectly predicts the depth of the scene depicted on the flat print. Our
    method is able to correct this error.}
	\label{fig:results_captured}
\end{figure}

>>>>

% The laser operates at 450~nm with a pulse repetition rate of 25~MHz with a peak power of 450~mW and average power of 0.5~mW.
\begin{figure}[t]
	\centering
  \includegraphics[width=0.4\columnwidth]{prototype_single_col.pdf}
  \caption{Prototype scanning setup. The pulsed light from the laser travels
    through a beam splitter before being guided by the galvo to the scene.
    Returning light is measured by the single-pixel SPAD. The Kinect v2 RGB 
    camera is used to capture the image used to generate the monocular depth estimate
    (the depth camera is not used).}
  \label{fig:prototype}
  % \vspace{-0.5em}
\end{figure}

@@

\begin{figure}[t]
	\centering
  \includegraphics[width=0.8\columnwidth]{scanned_diffuse.pdf}
  \caption{Scene and measurements for diffused and summed scanned mode. The observed
    counts in the diffuse mode match closely with the sum of the raster-scanned
    measurements. \edit{PLEASE EDIT THIS FIGURE TO MAKE BOTH PANELS THE SAME HEIGHT. MAYBE JUST COMBINE IT WITH THE PROTOTYPE INTO A SINGLE 2-PANEL FIGURE.}}
  \label{fig:scanned_diffuse}
  % \vspace{-0.5em}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Experimental Results}
\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{captured.pdf}
	\caption{Experimental results. For each scene, we record a ground truth depth
    map that is raster-scanned with the SPAD (upper left subimages), and an RGB
    image (lower left). A monocular depth CNN predicts an initial depth map (top
    middle), which is corrected with the diffused SPAD histogram using the
    proposed method (top right), as shown by the error maps and root mean
    squared error (RMSE) for each example (lower center, right). The CNN is
    confused when we show it a photograph of a poster (bottom scene); it
    incorrectly predicts the depth of the scene depicted on the flat print. Our
    method is able to correct this error.}
	\label{fig:results_captured}
\end{figure}

@@

### 2020-02-28 paper/eccv2020/sections/introduction.tex
pass over paper

\begin{figure}[t]
  \centering
  \includegraphics[width=0.3\columnwidth]{teaser.pdf}
  \caption{Monocular depth estimation predicts a depth map (upper right) from a
    single RGB image (upper left). The ill-posedness of the problem prevents
    reliable absolute depth estimation, resulting in large errors (inset image).
    The proposed method uses a \edit{single transient measurement aggregating the time-of-flight information of the entire scene (lower left)} to correct the output of the depth estimation and optimize the quality of the
    estimated absolute depth (lower right).}
  \label{fig:teaser}
\end{figure}

Traditional depth sensing techniques include those based on stereo or multiview,
active illumination, camera motion, or focus cues~\cite{szeliski2010computer}.
However, each of these techniques has aspects that may make their deployment
challenging. For example, stereo or multiview techniques require multiple
cameras, active illumination techniques may have limited resolution or require
time-consuming scanning procedures, and other techniques require camera motion
or multiple exposures at different focus distances.

One of the most promising approaches to overcoming these challenges is monocular
depth estimation (MDE), which requires only a single RGB image from a
conventional camera to recover a dense depth
map~\cite{Alhashim2018,Eigen2014,Fu2018,Laina2016,Saxena2006}. Recent approaches
to MDE employ neural network models that learn to predict depth by exploiting
monocular image cues such as perspective, occlusion, shading, and relative
object size. While such models have significantly improved over recent years,
MDE approaches to date are incapable of reliably estimating absolute distances
in a scene due to the inherent scale ambiguities of monocular image cues.
Instead, these models excel in predicting ordinal depth, or the relative
ordering of objects in a scene~\cite{Eigen2014,Fu2018}. Interestingly, Alhashim
and Wonka~\cite{Alhashim2018} recently showed that if the median ground truth
depth of the scene is known, the initial output of a MDE network can be
corrected to produce accurate absolute depth.

@@

Although access to the median ground truth depth is impossible in a realistic
scenario, low-cost sensors capable of capturing aggregated depth information
from a scene are readily available. For example, the proximity sensor on recent
generation Apple iPhones uses a low-power pulsed light source and a
single-pixel \edit{time-resolved detector} %, single-photon avalanche diode (SPAD) 
to sense distance to an
object directly in front of the phone. %SPADs 
\edit{
Time-resolved detectors, such as avalanche photon diodes (APDs) or single-photon avalanche diodes (SPADs), measure the full waveform of time-resolved incident radiance at each pixel. These detectors form the backbone of modern LiDAR
systems~\cite{Kirmani:2014,Li:2019,pawlikowska2017single}. However, single-photon sensor arrays} have
not been used for 3D imaging on consumer electronics because the requirement for
ultra-fast timing electronics makes it difficult to produce high-resolution
arrays at low cost, and because the scanning requirement for single-pixel
systems introduces a point of mechanical failure and complicates
high-resolution, high-framerate imaging.

@@

Here, we propose to use a single-pixel \edit{time-resolved detector} and pulsed light source in an
unconventional way: rather than optically focusing them to record the distance
to a single scene point, we diffuse the emitted light and \edit{aggregate the reflected light over the
entire scene with the detector}. The resulting \edit{transient} measurement resembles a histogram of the depth of
the scene and we demonstrate that this can be used to achieve accurate absolute
depth when combined with the estimate of \edit{any monocular depth estimator in a post-processing step} (\cf~Figure~\ref{fig:teaser}).

@@

To this end, we develop a sensor fusion strategy that processes the ordinal
depth computed by a monocular depth estimator to be consistent with the
measurements captured by the \edit{aggregated time-resolved} detector. We demonstrate in extensive
simulations that our approach achieves substantial improvements in the quality
of the estimated depth maps, regardless of which specific depth estimator is
used. \edit{Moreover, we build an camera prototype that combines an RGB camera and a single-pixel time-resolved detector.}  With this
work, we present a practical way to disambiguate depth estimation with RGB
images using minimal additional sensing hardware. Specifically, we make the
following contributions:
%
\begin{itemize}
	\item We propose augmenting an RGB camera with a global depth histogram \edit{aggregated by a diffused time-resolved detector} to address scale ambiguity error in monocular depth estimators.	
  \item We analyze this approach on indoor scenes using the NYU Depth v2 dataset and demonstrate that our approach is able to resolve scale ambiguity while being fast and easy to implement.
	\item We build a prototype camera and evaluate its efficacy on captured data, assessing both the quality and the ability of our method to help generalization of monocular depth estimators across scene types. 
\end{itemize}

\edit{\emph{Overview of Limitations:} our prototype camera uses a scanned SPAD and digitally aggregates the captured transients to emulate a single diffused measurement. The benefit of this approach is that we have access to ground truth depth, allowing us to evaluate the efficacy of our method with measured data. However, when operating SPADs in certain conditions, they may observe a nonlinear aggregation effect known as pileup. In these conditions, the emulated measurements may differ from a single optically diffused measurement. Yet, we experimentally verify that digitally and optically aggregated measurements captured with our system are very similar and pileup could also be computationally corrected~\cite{Heide:2018,Rapp:2019}, although we did not attempt to do this.}

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=0.3\columnwidth]{teaser.pdf}
  \caption{Monocular depth estimation predicts a depth map (upper right) from a
    single RGB image (upper left). The ill-posedness of the problem prevents
    reliable absolute depth estimation, resulting in large errors (inset image).
    The proposed method uses a \edit{single transient measurement aggregating the time-of-flight information of the entire scene (lower left)} to correct the output of the depth estimation and optimize the quality of the
    estimated absolute depth (lower right). \edit{PLEASE CHANGE FIGURE LAYOUT!}}
  \label{fig:teaser}
\end{figure}

Traditional depth sensing techniques include those based on stereo or multiview,
active illumination, camera motion, or focus cues~\cite{szeliski2010computer}.
However, each of these techniques has aspects that may make their deployment
challenging \edit{in certain scenarios}. For example, stereo or multiview techniques require multiple
cameras, active illumination techniques may have limited resolution or require
time-consuming scanning procedures, and other techniques require camera motion
or multiple exposures at different focus distances.

One of the most promising approaches to overcoming these challenges is monocular
depth estimation (MDE), which requires only a single RGB image from a
conventional camera to recover a dense depth
map~\cite{Alhashim2018,Eigen2014,Fu2018,Laina2016,Saxena2006}. Recent approaches
to MDE employ neural networks that learn to predict depth by exploiting
\edit{pictorial depth} cues such as perspective, occlusion, shading, and relative
object size. While such models have significantly improved over recent years,
MDE approaches to date are incapable of reliably estimating absolute distances
in a scene due to the inherent scale ambiguities of monocular image cues.
Instead, these models excel in predicting ordinal depth, or the relative
ordering of objects in a scene~\cite{Eigen2014,Fu2018}. Interestingly, Alhashim
and Wonka~\cite{Alhashim2018} recently showed that if the median ground truth
depth of the scene is known, the initial output of a MDE network can be
corrected to produce accurate absolute depth.

@@

Although access to the median ground truth depth is impossible in a realistic
scenario, low-cost sensors capable of capturing aggregated depth information
from a scene are readily available. For example, the proximity sensor on recent
generation Apple iPhones uses a low-power pulsed light source and a
single-pixel \edit{time-resolved detector} %, single-photon avalanche diode (SPAD) 
to sense distance to an
object directly in front of the phone. %SPADs 
\edit{
Time-resolved detectors, such as avalanche photon diodes (APDs) or single-photon avalanche diodes (SPADs), measure the full waveform of time-resolved incident radiance at each pixel (Fig.~\ref{fig:teaser}). These detectors form the backbone of modern LiDAR
systems~\cite{Kirmani:2014,Li:2019,pawlikowska2017single}. However, single-photon sensor arrays} have
not yet been used for 3D imaging on consumer electronics, primarily because the requirement for
ultra-fast timing electronics makes it difficult to produce high-resolution
arrays at low cost and because the scanning requirement for single-pixel
systems introduces a point of mechanical failure and complicates
high-resolution, high-framerate imaging.

@@

Here, we propose to use a single-pixel \edit{time-resolved detector} and pulsed light source in an
unconventional way: rather than optically focusing them to record the distance
to a single scene point, we diffuse the emitted light and \edit{aggregate the reflected light over the
entire scene with the detector}. The resulting \edit{transient} measurement resembles a histogram of the scene depth and we demonstrate that this can be used to achieve accurate absolute
depth when combined with the estimate of \edit{any monocular depth estimator in a post-processing step} (Fig.~\ref{fig:teaser}).

@@

To this end, we develop a sensor fusion strategy that processes the ordinal
depth computed by a monocular depth estimator to be consistent with the
measurements captured by the \edit{aggregated time-resolved} detector. We demonstrate in extensive
simulations that our approach achieves substantial improvements in the quality
of the estimated depth maps, regardless of which specific depth estimator is
used. \edit{Moreover, we build an camera prototype that combines an RGB camera and a single-pixel time-resolved detector.}  With this
work, we present a practical way to disambiguate depth estimation with RGB
images using minimal additional sensing hardware. Specifically, we make the
following contributions:
%
\begin{itemize}
	\item We propose augmenting an RGB camera with a global depth histogram \edit{aggregated by a time-resolved detector} to address scale ambiguity error in monocular depth estimators.	
  \item We analyze this approach on indoor scenes using the NYU Depth v2 dataset and demonstrate that our approach is able to resolve scale ambiguity while being fast and easy to implement.
	\item We build a prototype camera and evaluate its efficacy on captured data, assessing both the quality and the ability of our method to help generalization of monocular depth estimators across scene types. 
\end{itemize}

\edit{\emph{Overview of Limitations:} our prototype camera uses a scanned SPAD and digitally aggregates the captured transients to emulate a single optically diffused measurement. The benefit of this approach is access to ground truth depth, allowing us to evaluate the efficacy of our method with measured data. However, when operating SPADs in certain conditions, they may observe a nonlinear aggregation effect known as pileup. In these conditions, the aggregated measurements may differ from a single optically diffused measurement. Yet, we experimentally verify that digitally and optically aggregated measurements captured with our system are very similar and pileup could also be computationally corrected~\cite{Heide:2018,Rapp:2019}, although we did not attempt this.}

### 2020-02-28 paper/eccv2020/sections/method.tex
pass over paper

In this section, we describe the image formation of a diffused pulsed laser and single-photon avalanche diode (SPAD). We also describe an approach for correcting a depth map generated with a monocular depth estimator to match the global scene information captured by the SPAD.

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.6\columnwidth]{method.pdf}
  \caption{Overview of processing pipeline. The processing pipeline uses
      the input SPAD measurements and an RGB image to produce an accurate depth
      map. The SPAD measurements are preprocessed to adjust for ambient photon
      detections, radiometric falloff factors, and to calibrate the bin widths.
      From the RGB image, an MDE estimates an initial depth map
      and the scene reflectance is estimated. A reflectance-weighted
      depth histogram is compared to the processed SPAD measurements to
      calculate a histogram matching matrix which is used to output the corrected depth.
  }
  \label{fig:pipeline}
\end{figure}

@@

While simply subtracting $\hat{b}$ from the measurements would remove many of
the background counts, a large number of bins containing only background counts would still
have non-zero values, resulting in a skewed
estimate after applying histogram matching.  Instead, we estimate the temporal
support of transient bins containing signal photons (\ie the range of depths in the
scene) and only subtract $\hat{b}$ from these bins (clipping negative bin values
to 0). We assume that other
transient bins contain only background counts that can be discarded.

@@

\vspace{0.8em}\noindent{\bf Falloff Compensation.}
In the second step, we compensate for distance falloff effects by multiplying
the transient
by the distance-dependent scaling factor,
\begin{equation}
    h'[n] = h[n] \cdot z_n^2.
  \label{eq:h_scaled}
\end{equation}
Here, $z_n= \paren*{n + \frac12}\paren*{\frac{c\Delta t}{2}}$ is the distance
corresponding to bin $n$, and this radiometric falloff model is consistent with
measurements captured with our hardware prototype.

\vspace{0.8em}\noindent{\bf Transient Re-binning.}
Last, we re-bin the transient so that the bin widths increase for increasingly
distant objects. We select the Spacing-Increasing Discretization
(SID) method of \cite{Fu2018}, which changes the bin widths according to an  
exponential function, allocating more bins to closer distances and fewer
bins to farther distances for a fixed number of bins. The bin edges $t_i$ are
given by the following equation,
parameterized by the number of bins $K$ and the range of distances $[\ell, u]$: 
\begin{equation}
  t_i = e^{\log(\ell) + \frac{\log(u/\ell) \cdot i}{K}}  \qquad\text{for}\qquad i = 0,\ldots, K.
  \label{eq:sid_bin_edges}
\end{equation}
This rebinning procedure allows us to use a reduced number of bins in the histogram
matching procedure, reducing computation time while maintaining accuracy.
\edit{For the simulated results we use $K = 140$ bins with $(\ell,
u)$ corresponding to the depth values of bins $\hat n_{\text{first}}$ and $\hat
n_{\text{last}}$ respectively.}
 The output of the rebinning procedure is the
target histogram $h_\text{target}$ which we use for histogram matching.

@@

\subsection{Histogram Matching}
% \begin{algorithm}[H]
%  \caption{Exact Histogram Matching} 
%  \label{alg:ehm}
%  \input{sections/figures/exact_hist_matching_pseudo.tex}
% \end{algorithm}
{ \footnotesize
\begin{algorithm}
 \caption{Find Pixel Movement} 
 \label{alg:ehm}
 \begin{algorithmic}
	\footnotesize
  \Procedure{FindPixelMovement}{$h_s$ of length $M$, $h_t$ of length $N$} 
    \State Initialize $T$ as an $M \times N$ array of zeros.
    \For{$m$ in $1,\ldots,M$}
      \For{$n$ in $1,\ldots,N$}
        \State $p_s \gets \sum_{i=1}^{n-1} T[m, i]$
        \State $p_t \gets \sum_{i=1}^{m-1} T[i, n]$
        \State $T[m, n] \gets \min(h_s[m] - p_s, h_t[n] - p_t)$
      \EndFor
    \EndFor
    \State \textbf{return} $T$
  \EndProcedure
 \end{algorithmic}
\end{algorithm}
}

@@

The input depth map cannot be directly histogram-matched to the target histogram
because the target histogram incorporates the spatially varying reflectance of
the scene. To account for reflectance in the histogram matching procedure,
we use the normalized image color channel closest to the laser wavelength as an
estimate of the reflectance and compute a reflectance-weighted depth histogram
$h_\text{source}$;
instead of incrementing a bin in the depth histogram by one for every pixel in the MDE
at the corresponding depth, we add the estimated reflectance value of the pixel
to the histogram bin. \edit{We also re-bin this histogram, again following Fu et al.\
and using $K = 140$ with $(\ell, u) = (0.657, 9.972)$~\cite{Fu2018}.}

@@

Finally, we use the movement matrix $T$ to shift the pixels of the input depth map
to match the global depth of the target histogram. For a depth map pixel with
depth bin $k$, we select the corrected bin by sampling from the distribution $T[k,
:]/\sum_{n=1}^NT[k,n]$. This sampling procedure handles the
case where a single input depth bin of the MDE is mapped to
multiple output bins~\cite{Morovic2002}.
%

>>>>

In this section, we describe the image formation of a diffused pulsed laser and time-resolved detector. \edit{Although our model is derived for the specific case of imaging with a single-photon avalanche diode (SPAD), the resulting image formation model equally applies to other time-resolved detectors}. We also describe an approach for correcting a depth map generated with a monocular depth estimator to match the global scene information captured by the \edit{transient}.

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.6\columnwidth]{method.pdf}
  \caption{Overview of processing pipeline. The processing pipeline uses
      the input \edit{transient measurement} and an RGB image to produce an accurate depth
      map. The \edit{transient is} preprocessed to adjust for ambient photon
      detections, radiometric falloff factors, and to calibrate the bin widths.
      From the RGB image, an MDE estimates an initial depth map
      and the scene reflectance is estimated. A reflectance-weighted
      depth histogram is compared to the processed \edit{transient} to
      calculate a histogram matching matrix which is used to output the corrected depth. \edit{PLEASE CHANGE FIGURE LAYOUT!}
  }
  \label{fig:pipeline}
\end{figure}

@@

While simply subtracting $\hat{b}$ from the measurements would remove many of
the background counts, a large number of bins containing only background counts would still
have non-zero values, resulting in a skewed
estimate after applying histogram matching.  Instead, we estimate the temporal
support of transient bins containing signal photons (\ie, the range of depths in the
scene) and only subtract $\hat{b}$ from these bins (clipping negative bin values
to 0). We assume that other
transient bins contain only background counts that can be discarded.

@@

\vspace{0.8em}\noindent{\bf Falloff Compensation.}
In the second step, we compensate for distance falloff effects by multiplying
the transient
by the distance-dependent scaling factor,
%
\begin{equation}
    h'[n] = h[n] \cdot z_n^2.
  \label{eq:h_scaled}
\end{equation}
%
Here, $z_n= \paren*{n + \frac12}\paren*{\frac{c\Delta t}{2}}$ is the distance
corresponding to bin $n$, and this radiometric falloff model is consistent with
measurements captured with our prototype.

\vspace{0.8em}\noindent{\bf Transient Re-binning.}
Last, we re-bin the transient so that the bin widths increase for increasingly
distant objects. We select the Spacing-Increasing Discretization
(SID) method of \cite{Fu2018}, which changes the bin widths according to an  
exponential function, allocating more bins to closer distances and fewer
bins to farther distances for a fixed number of bins. The bin edges $t_i$ are
given by the following equation,
parameterized by the number of bins $K$ and the range of distances $[\ell, u]$: 
%
\begin{equation}
  t_i = e^{\log(\ell) + \frac{\log(u/\ell) \cdot i}{K}}  \qquad\text{for}\qquad i = 0,\ldots, K.
  \label{eq:sid_bin_edges}
\end{equation}
%
This rebinning procedure allows us to use a reduced number of bins in the histogram
matching procedure, reducing computation time while maintaining accuracy.
\edit{For the simulated results we use $K = 140$ bins with $(\ell,
u)$ corresponding to the depth values of bins $\hat n_{\text{first}}$ and $\hat
n_{\text{last}}$ respectively.}
 The output of the rebinning procedure is the
target histogram $h_\text{target}$ which we use for histogram matching.

@@

\subsection{Histogram Matching}
% \begin{algorithm}[H]
%  \caption{Exact Histogram Matching} 
%  \label{alg:ehm}
%  \input{sections/figures/exact_hist_matching_pseudo.tex}
% \end{algorithm}
{ \footnotesize
\begin{algorithm}
 \caption{Find Pixel Movement \edit{MOVE TO SUPPLEMENT!}} 
 \label{alg:ehm}
 \begin{algorithmic}
	\footnotesize
  \Procedure{FindPixelMovement}{$h_s$ of length $M$, $h_t$ of length $N$} 
    \State Initialize $T$ as an $M \times N$ array of zeros.
    \For{$m$ in $1,\ldots,M$}
      \For{$n$ in $1,\ldots,N$}
        \State $p_s \gets \sum_{i=1}^{n-1} T[m, i]$
        \State $p_t \gets \sum_{i=1}^{m-1} T[i, n]$
        \State $T[m, n] \gets \min(h_s[m] - p_s, h_t[n] - p_t)$
      \EndFor
    \EndFor
    \State \textbf{return} $T$
  \EndProcedure
 \end{algorithmic}
\end{algorithm}
}

@@

The input depth map cannot be directly histogram-matched to the target histogram
because the target histogram incorporates the spatially varying reflectance of
the scene. To account for reflectance in the histogram matching procedure,
we use the normalized image color channel closest to the laser wavelength as an
estimate of the reflectance and compute a reflectance-weighted depth histogram
$h_\text{source}$;
instead of incrementing a bin in the depth histogram by one for every pixel in the MDE
at the corresponding depth, we add the estimated reflectance value of the pixel
to the histogram bin. \edit{We also re-bin this histogram, following Fu et al. and using $K = 140$ with $(\ell, u) = (0.657, 9.972)$~\cite{Fu2018}.}

@@

Finally, we use the movement matrix $T$ to shift the pixels of the input depth map
to match the global depth of the target histogram. For a depth map pixel with
depth bin $k$, we select the corrected bin by sampling from the distribution $T[k,
:]/\sum_{n=1}^NT[k,n]$. This sampling procedure handles the
case where a single input depth bin of the MDE is mapped to
multiple output bins~\cite{Morovic2002}.

\edit{Pseudo-code for this procedure is included in the supplement; we will make source code and data available.}

### 2020-02-28 paper/eccv2020/sections/related.tex
pass over paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Monocular Depth Estimation}
%
Estimating a depth map from a single RGB image has been approached using Markov
Random Fields~\cite{Saxena2006}, geometric approaches~\cite{Hoiem2005}, and
non-parametric, SIFT-based methods~\cite{Karsch2014}. More recently, deep neural
networks have been applied to this problem. For example, Eigen et
al.~\cite{Eigen2014} use a multi-scale neural network to predict depth maps,
Godard et al.~\cite{Godard2017} use an unsupervised approach that trains a
network using stereo pairs, and Fu et al.~\cite{Fu2018} combine a logarithmic
depth discretization scheme with an ordinal regression loss function. Various
experiments using different types of encoder networks (\eg ResNet,
DenseNet)~\cite{Alhashim2018,Laina2016} have also been employed with some
success, as have approaches mixing deep learning with conditional random
fields~\cite{Xu2017}, and attention-based approaches~\cite{Hao2018,Xu2018}.
Recently, Lasinger et al.~\cite{Lasinger:2019} improved the robustness of
monocular depth estimation using cross-dataset transfer.

Despite achieving remarkable success on estimating ordinal depth from a single
image, none of these methods are able to resolve inherent scale ambiguity in a
principled manner. We introduce a new approach that leverages existing monocular
depth estimation networks and disambiguates the output using depth
histogram-like measurements obtained from a single, diffused SPAD. Other
approaches to disambiguating monocular depth estimation use optimized freeform
lenses~\cite{Chang:2019:DeepOptics3D,Wu:2019} or dual-pixel
sensors~\cite{Garg:2019}, but these approaches require custom lenses or sensors
and specialized image reconstruction methods. \edit{In contrast, our approach adds
minimal additional hardware to a single RGB camera, and leverages sensors currently
deployed in consumer electronics.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Depth Imaging and Sensor Fusion with SPADs}
%
Emerging single-photon LiDAR systems use single-photon avalanche diodes (SPADs)
to record the time of flight of individual photons. SPAD detectors can be
fabricated using standard CMOS processes, but the required picosecond-accurate
time-stamping electronics are challenging to miniaturize and fabricate at low
cost. For this reason, many single-photon 3D imaging approaches use a single
SPAD combined with a raster scanning
mechanism~\cite{Kirmani:2014,Lamb2010,Li:2019,pawlikowska2017single,gupta2019photonflooded}.
Unfortunately, this makes it challenging to scan dynamic scenes at high
resolution and scanners can also be expensive, difficult to calibrate, and prone
to mechanical failure. To reduce the scanning complexity to one dimension, 1D
SPAD arrays have been
developed~\cite{burri2017linospad,burri2016linospad,OToole2017}, and 2D SPAD
arrays are also an active area of
research~\cite{Niclass2005,Stoppa2007,Veerappan2011,Zhang2018}. Yet,
single-pixel SPADs remain the only viable option for low-cost consumer devices
today.

The proposed method uses a single-pixel SPAD and pulsed light source that are
diffused across the entire scene instead of aimed at a single point, as with
proximity sensors. This unique configuration captures a measurement that closely
resembles the depth histogram of the scene. Our sensor fusion algorithm achieves
reliable absolute depth estimation by combining the SPAD measurement with the
output of a monocular depth estimator using a histogram matching technique.
While other recent work also explored RGB-SPAD sensor fusion~\cite{Lindell2018},
the RGB image was primarily used to guide the denoising and upsampling of
measurements from a SPAD array.

@@

In our procedure, the diffused SPAD measurements closely resemble a histogram of
the depth map where the histogram values are weighted by spatially varying scene
reflectances and inverse-square falloff effects. We therefore adapt the
algorithm in Morovic et al.~\cite{Morovic2002} in order to accommodate general
per-pixel weights during histogram matching.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Monocular Depth Estimation}
%
Estimating a depth map from a single RGB image has been approached using Markov
Random Fields~\cite{Saxena2006}, geometric approaches~\cite{Hoiem2005}, and
non-parametric, SIFT-based methods~\cite{Karsch2014}. More recently, deep neural
networks have been applied to this problem, \edit{for example using a multi-scale neural network to predict depth maps~\cite{Eigen2014},
using an unsupervised approach that trains a network using stereo pairs~\cite{Godard2017}, and using a logarithmic
depth discretization scheme combined with an ordinal regression loss function~\cite{Fu2018}}. Various
experiments using different types of encoder networks (\eg, ResNet,
DenseNet)~\cite{Alhashim2018,Laina2016} have also been employed with some
success, as have approaches mixing deep learning with conditional random
fields~\cite{Xu2017}, and attention-based approaches~\cite{Hao2018,Xu2018}.
Recently, Lasinger et al.~\cite{Lasinger:2019} improved the robustness of
monocular depth estimation using cross-dataset transfer.

Despite achieving remarkable success on estimating ordinal depth from a single
image, none of these methods is able to resolve inherent scale ambiguity in a
principled manner. We introduce a new approach that leverages existing monocular
depth estimation networks and disambiguates the output using depth
histogram--like measurements obtained from a single \edit{time-resolved detector}. Other
approaches to disambiguating monocular depth estimation use optimized freeform
lenses~\cite{Chang:2019:DeepOptics3D,Wu:2019} or dual-pixel
sensors~\cite{Garg:2019}, but these approaches require custom lenses or sensors
and specialized image reconstruction methods. \edit{In contrast, our approach adds
minimal additional hardware to a single RGB camera, and may leverage sensors currently
deployed in consumer electronics.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Depth Imaging and Sensor Fusion with Time-resolved Detectors}
%
\edit{Emerging LiDAR systems use avalanche photon diodes (APDs) or single-photon avalanche diodes (SPADs)
to record the time of flight of individual photons. These time-resolved detectors} can be
fabricated using standard CMOS processes, but the required time-stamping electronics are challenging to miniaturize and fabricate at low
cost. For this reason, many \edit{LiDAR systems}, especially those using SPADs, use a single \edit{or a few detectors}
combined with a  scanning
mechanism~\cite{Kirmani:2014,Lamb2010,Li:2019,pawlikowska2017single,gupta2019photonflooded}.
Unfortunately, this makes it challenging to scan dynamic scenes at high
resolution and scanners can also be expensive, difficult to calibrate, and prone
to mechanical failure. To reduce the scanning complexity to one dimension, \edit{1D
detector arrays} have been
developed~\cite{burri2017linospad,burri2016linospad,OToole2017}, and 2D SPAD arrays are also an active area of
research~\cite{Niclass2005,Stoppa2007,Veerappan2011,Zhang2018}. Yet,
single-pixel \edit{time-resolved detectors} remain the only viable option for low-cost consumer devices
today.

The proposed method uses a single-pixel \edit{APD or SPAD} and pulsed light source that are
diffused across the entire scene instead of aimed at a single point, as with
proximity sensors. This unique configuration captures a measurement that closely
resembles the depth histogram of the scene. Our sensor fusion algorithm achieves
reliable absolute depth estimation by combining the \edit{transient} measurement with the
output of a monocular depth estimator using a histogram matching technique.
While other recent work also explored RGB-SPAD sensor fusion~\cite{Lindell2018},
the RGB image was primarily used to guide the denoising and upsampling of
measurements from a SPAD array.

@@

In our procedure, the \edit{transient measurements} closely resemble a histogram of
the depth map where the histogram values are weighted by spatially varying scene
reflectances and inverse-square falloff effects. We therefore adapt the
algorithm in Morovic et al.~\cite{Morovic2002} in order to accommodate general
per-pixel weights during histogram matching.
